Interpretable Machine Learning

### 2017-11-29 talk.Rmd
finish first draft of slides

---
title: "Interpretable Machine Learning"
author: "Christoph Molnar"
date: "December 11, 2017"
output: ioslides_presentation
---

## 
Scenario: A company approaches you to predict data scientist salaries with machine learning.

![](images/wow.jpg)

@@

![](images/magic.jpg)

## Step 1: Find some data
Kaggle conducted an industry-wide survey of data scientists. 
Questions asked:

- Demographic
- Salary
- Are you currently enrolled as a student at a degree granting school?	
- How adequately do you feel your title describes what you do (or what you did if retired)?	
- How long have you been learning data science?

TODO: Add only relevant questions here for analysis

@@

## Step 2: Throw ML on your data
```{r learn, warning=FALSE}
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
n = getTaskSize(task)
lrn = makeLearner('regr.randomForest', importance=TRUE)
mod = train(lrn, task, subset = seq(1, n, 2))
pred = predict(mod, task = task, subset = seq(2, n, 2))
## TODO: Find better variables https://www.kaggle.com/kaggle/kaggle-survey-2017/data
```
## Step 3: Profit. We are done! {.center}

@@

## "There is a problem with the model!"
```{r, echo=FALSE, out.width='100%', fig.align='center'}
knitr::include_graphics("images/Hide-the-pain-harold-phone.jpg")
```

@@

## "We want to understand the model better!"

@@

## Gender?!
```{r, echo=FALSE, fig.align='center', out.width='60%'}
knitr::include_graphics("images/big-mistake.png")
```

@@

```{r}
pdp = generatePartialDependenceData(mod, task, features =c('GenderSelect'))
knitr::kable(pdp$data)
```

@@

## "We want to understand each decision!"

@@

## Interpretability
- The degree to which an observer can understand the cause of a decision.
- Current state in machine learning: Minimize loss, get best prediction, ignore interpretation
- Current state in statistics: Fit model, interpret output, ignore predictive performance
- Ideal world: Get best predictive performance + interpretability

## When is it important
Interpretability of machine learning models is when the problem is fundamentally underspecified.

## Book
Interested in learning more!

@@

>>>>

---
title: "Interpretable Machine Learning"
author: "Christoph Molnar"
date: "December 4, 2017"
output:
  ioslides_presentation:
    css: styles.css
---

##  {.emphasizedabit}
Scenario: A company approaches you to predict data scientist salaries with machine learning.

```{r, echo=FALSE, fig.align='center'}
knitr::include_graphics("images/wow.jpg")
```

@@

```{r, echo=FALSE, fig.align='center'}
knitr::include_graphics("images/magic.jpg")
```

## Step 1: Find some data
Kaggle conducted an industry-wide survey of data scientists. 
https://www.kaggle.com/kaggle/kaggle-survey-2017

Information asked:

- Compensation
- Demographics
- Job title
- Experience
- ...

@@

## Step 2: Throw ML on your data
```{r learn, warning=FALSE}
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
lrn = makeLearner('regr.randomForest', importance=TRUE)
mod = train(lrn, task)
```
## Step 3: Profit. We are done! {.center}

@@

##  {.emphasizedabit}

"There is a problem with the model!"

## What problem?

```{r, echo=FALSE, out.width='100%', fig.align='center'}
knitr::include_graphics("images/Hide-the-pain-harold-phone.jpg")
```

@@

##  {.emphasizedabit}

"We want to understand the model better!"

@@

## Gender?!
```{r, echo=FALSE, fig.align='center', out.width='80%'}
knitr::include_graphics("images/big-mistake.png")
```

@@

```{r}
pdp = generatePartialDependenceData(mod, task, features =c('Gender'))
ggplot(pdp$data) + geom_point(aes(x=Gender, y=CompensationAmount)) + 
  geom_segment(aes(x=Gender, xend=Gender, yend=CompensationAmount), y=0) + 
  scale_y_continuous(limits=c(0, NA)) + 
  theme(axis.text.x = element_text(angle = 10, hjust = 1))
```

```{r, echo=FALSE, fig.align='center', out.width='100%'}
knitr::include_graphics("images/facepalm.gif")
```

@@

```{r, echo=FALSE, fig.align='center', out.width='40%'}
knitr::include_graphics("images/angry.gif")
```

@@

## Interested in learning more?

@@

```{r, echo=FALSE, fig.align='center', out.width='80%'}
knitr::include_graphics("images/book.png")
```
